Differentiable Optics with dLux: I - Deep Calibration of Flat Field and Phase with Automatic Differentiation

### 2022-11-10 src/tex/ms.tex
[showyourwork] overleaf sync

\renewcommand{\baselinestretch}{1.0} % Change to 1.65 for double spacing
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
% \usepackage{relsize}
\usepackage{acro}
\acsetup{
  single    = false,
  list/sort  = true,
  cite/group = true,
  cite/group/cmd = \cite,
  cite/group/pre = {},
}

@@

\newcommand\jax{\textsc{Jax}\xspace}
\newcommand\dlux{$\partial$Lux\xspace}

\title{Differentiable Optics with {\Large $\partial$}Lux: I - Deep Calibration of Flat Field and Phase with Automatic Differentiation}

@@

High-precision, high-cadence time series of space photometry from \textit{Kepler} \cite{Borucki2010}, K2 \cite{K2}, TESS \cite{TESS} and CHEOPS \cite{CHEOPS} space telescopes have been revolutionary for exoplanetary science and stellar astrophysics.

@@

%  flat field calibration
Much work has been put towards developing data-driven self-calibration of the flat field in K2, which are of general interest and applicability for other space photometry missions. 
% 		- self-flat fielding (Andrew Vanderburg) 
\citet{self_flat-fielding} developed the `self flat-fielding' approach that harnesses the correlation between causally-disconnected sources in order to isolate the noise processes of interest. First the thruster firings and pointing drift is calibrated by calculating the correlation between all stellar sources on the detector. Time-series photomtetric signals that correlate with source position are then used to isolate the signal introduced by pixel sensitivity variation and correct for it.
%       - dun wang causal pixel model 
Taking a similar approach \citet{causal_pixel} constrains instrumental effects by measuring correlations in the light curves of causally uncorrelated pixels.
% 		- Christina Hedges (pixel cal papers) ??
% 		- Luger papers (pixel-level decorrelation)
In \citet{pixel_decorr} ... 
% 		- halo photometry (white, pope)
Other non-linear instrumental effects such as saturation can further complicate the recovery of precise light curves. Halo photometry \citep{halo, halo2} sidesteps the saturation problem by extracting light curves from the `halo' of scattered light around the saturated pixels. Instrumental and astrophysical effects are separated by assigning individual pixel weights and biases, which are optimised in order to maximise correlation the between pixel light-curves within the same halo, and minimise correlations between pixels light curves across different halos.

>>>>

\renewcommand{\baselinestretch}{1.0} % Change to 1.65 for double spacing
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{hyperref}
\usepackage{relsize}
\usepackage{acro}
\acsetup{
  single    = false,
  list/sort  = true,
  cite/group = true,
  cite/group/cmd = \cite,
  cite/group/pre = {},
}

@@

% \newcommand\jax{\textsc{Jax}\xspace}
\newcommand\dlux{$\partial$Lux\xspace}

% \title{Differentiable Optics with {\Large $\partial$}Lux: I - Deep Calibration of Flat Field and Phase with Automatic Differentiation}
\title{Differentiable Optics with dLux: I - Deep Calibration of Flat Field and Phase with Automatic Differentiation}

@@

High-precision, high-cadence time series of space photometry from \textit{Kepler} \cite{Borucki2010}, K2 \cite{K2}, TESS \cite{TESS} and CHEOPS \cite{CHEOPS} space telescopes have been revolutionary for exoplanetary science \cite{Zhu2021} and stellar astrophysics \cite{Aerts21,Jackiewicz2021}.

@@

%  flat field calibration
Much work has been put towards developing data-driven self-calibration of the flat field in K2, which are of general interest and applicability for other space photometry missions. 
% 		- self-flat fielding (Andrew Vanderburg) 
In  `self flat-fielding' (K2SFF\cite{self_flat-fielding}), the light curve is decorrelated against principal components of all light curves on the detector. Time-series photometric signals that correlate with source position are then used to isolate the signal introduced by pixel sensitivity variation and correct for it.
%       - dun wang causal pixel model 
Taking a similar approach \citet{causal_pixel} constrains instrumental effects by measuring correlations in the light curves of causally uncorrelated pixels.
% 		- Christina Hedges (pixel cal papers) ??
% 		- Luger papers (pixel-level decorrelation)
In \citet{pixel_decorr} ... 
% 		- halo photometry (white, pope)
Other non-linear instrumental effects such as saturation can further complicate the recovery of precise light curves. Halo photometry \citep{halo, halo2} sidesteps the saturation problem by extracting light curves from the `halo' of scattered light around the saturated pixels. Instrumental and astrophysical effects are separated by assigning individual pixel weights and biases, which are optimised in order to maximise correlation the between pixel light-curves within the same halo, and minimise correlations between pixels light curves across different halos.
